STM single case

### 2019-04-12 Messy Code/Pillar 2 -(STM) Topic Modeling- Errors.Rmd

# keep most recent year
#d_text <- d_text %>% map(function(tb, y) tb %>% filter(year == max(year)))
```
###As corpus
```{r}

```
# TF-IDF
We will perform an initial (visual) exploratory analysis of our textual data using TF- IDF.

@@

  STM_model <- stm(corpus$documents, corpus$vocab, K = n_topics, init.type = "Spectral")
}
```
####My_stm_eval Function
This function applied stm but with heldout vocab and documents. 
```{r}
my_stm_eval <- function(heldout, n_topic){
  stm::stm(heldout$documents, heldout$vocab, n_topic, init.type = "Spectral")
}
```

@@

@@

stm_model <- tibble(
  #repeat each topic number twice (once for overview and once for manual)
  n_topic = rep(topic_numbers, each = 2) ) %>%
  mutate(
  #Identification information
  Origin     = rep(c("catalogues", "manuals"), length(topic_numbers)),         
  `Topic ID` = paste(Origin, n_topic, sep = "_"),
  #DTM

  DTM       = pmap(.l = list(Origin), .f = extract_dtm),

  doc_names = map(DTM, rownames),
  #STM Corpus
  Corpus           = pmap(.l = list(Origin),   .f = extract_corpus), 
  #Documents- STM corpus
  Documents_stm     = pmap(.l=list(Corpus),    .f = extract_documents),
  #Vocab- STM corpus
  Vocab_stm         = pmap(.l=list(Corpus),    .f = extract_vocab),
  #Data- STM corpus
  Data_stm          = pmap(.l=list(Corpus),    .f = extract_data),
  #Fit Model
  Model  = pmap(.l = list(n_topic, Corpus), .f = my_stm),

  #Evaluation
  Exclusivity        = map(Model, exclusivity),

  semantic_coherence = pmap(.l = list(Model,DTM), semanticCoherence, M = 10), #M = num. of top words per topic
  #Alretnative input to semantic_coherence = pmap(.l = list(Model, Documents_stm), semanticCoherence, M = 10),

  #
  ##Inspection
  #Beta distribution
  Beta = pmap(.l = list(Model),  .f = tidy),

  #Gamma distribution
  Gamma = pmap(.l = list(Model, DTM), .f = my_tidy_gamma), #fix this

@@

)

```
####TESTING AND INSPECTING MODELS
```{r model inspection}
my_test <-  stm_model %>% filter(n_topic == 10, Origin == "manuals")
```
####For evaluation
```{r models in tibble}
topic_numbers <-  seq(from = 5, to = 10, by = 5) #seq(from = 5, to = 150, by = 5)

@@

    lbound             = bound + lfact,
    iterations         = map_dbl(Model,       
                                 function(model) length(model$convergence$bound))
    ) 
```
###Saving Results
```{r save}
#saving
my_models <-  list(use = stm_model, eval = stm_eval_model)
save(my_models , file="STM_models.RDATA")
```

@@

plot.STM(test, "labels", topics = c(1:5))
```
#New Documents
##Align vocabulary
```{r align vocab}
#back up current code
d_text1 <- d_text

>>>>

# keep most recent year
#d_text <- d_text %>% map(function(tb, y) tb %>% filter(year == max(year)))
```

# TF-IDF
We will perform an initial (visual) exploratory analysis of our textual data using TF- IDF.

@@

  STM_model <- stm(corpus$documents, corpus$vocab, data = data, prevalence = ~department, ### ~department
                   K = n_topics, init.type = "Spectral")
}
```
####My_stm_eval Function
This function applied stm but with heldout vocab and documents. 
```{r}
my_stm_eval <- function(heldout, n_topic){
  stm::stm(heldout$documents, heldout$vocab, n_topic, init.type = "Spectral")
}
```

@@

#Extract covariates
extract_covariates <- function(origin) covariates %>% filter(Origin == origin) %>% pull(Data)

@@

stm_model 
preparation_for_model <- tibble(
  #repeat each topic number twice (once for overview and once for manual)
  n_topic = rep(topic_numbers, each = 2) ) %>%

  mutate(
    #Identification information
    Origin     = rep(c("catalogues", "manuals"), length(topic_numbers)),         
    `Topic ID` = paste(Origin, n_topic, sep = "_")) %>%

  #left_join(covariates, by = "Origin") %>%

  mutate(
    #DTM
    DTM       = pmap(.l = list(Origin), .f = extract_dtm),
    doc_names = map(DTM, rownames),

    #STM Corpus
    Corpus           = pmap(.l = list(Origin),   .f = extract_corpus), 
    #Documents- STM corpus
    #Documents_stm     = pmap(.l=list(Corpus),    .f = extract_documents),
    #Vocab- STM corpus
    #Vocab_stm         = pmap(.l=list(Corpus),    .f = extract_vocab),
    #Data- STM corpus
    #Data_stm          = pmap(.l=list(Corpus),    .f = extract_data),
    #Covariates
    Covariates        = pmap(.l = list(Origin),  .f = extract_covariates), # testing_model$Covariates[4][[1]][[1]]

    #clean_covariates
    clean_covariates = map(Covariates, .f = function(Covariates) Covariates[[1]]))

#iteration
this_model <- preparation_for_model %>% filter(n_topic==5, Origin=="manuals")

this_n_topic <- this_model$n_topic[[1]]
this_corpus <- this_model$Corpus[[1]]
this_clean_covariates <- this_model$clean_covariates[[1]]

this_model <- my_stm(this_n_topic, this_corpus, this_clean_covariates)

    #Fit Model  n_topics, corpus, data
    Model  = pmap(.l = list(n_topics = n_topic, corpus = Corpus, data = clean_covariates), 
                  .f = my_stm))

    #Evaluation
    Exclusivity        = map(Model, exclusivity),
    semantic_coherence = pmap(.l = list(Model,DTM), semanticCoherence, M = 10), #M = num. of top words per topic
    #Alretnative input to semantic_coherence = pmap(.l = list(Model, Documents_stm), semanticCoherence, M = 10),

    #
    ##Inspection

    #Beta distribution
    Beta = pmap(.l = list(Model),  .f = tidy),
    #Gamma distribution
    Gamma = pmap(.l = list(Model, DTM), .f = my_tidy_gamma), #fix this

@@

    #END MUTATE PARENTHESIS
         )

####For evaluation
```{r models in tibble}
topic_numbers <-  seq(from = 5, to = 10, by = 5) #seq(from = 5, to = 150, by = 5)

@@

    lbound             = bound + lfact,
    iterations         = map_dbl(Model,       
                                 function(model) length(model$convergence$bound))
    ) 
```
###Saving Results
```{r save}
#saving
save(list(use = stm_model, eval = stm_eval_model), file ="/Output/STM_models.RDATA")
```

@@

plot.STM(test, "perspectives", topics = c(1,5))
```
#New Documents
##Align vocabulary
```{r align vocab}
#back up current code
d_text1 <- d_text

### 2019-04-12 Messy Code/stm single case.Rmd

For `d_text` we keep only the most recent year.
```{r import data, eval = TRUE}
#load
load("/Users/sofia/Documents/DARS/GitDARS/Output/d_text.RDATA")
```

@@

  STM_model <- stm(corpus$documents, corpus$vocab, data= data, prevalence = ~department, K = n_topics, init.type = "Spectral")
}
```
####My_stm_eval Function
This function applied stm but with heldout vocab and documents. 
```{r}
my_stm_eval <- function(heldout, n_topic){
  stm::stm(heldout$documents, heldout$vocab, n_topic, init.type = "Spectral")
}
```

@@

Manuals_ models do not work:
```{r models_manuals in tibble}
topic_numbers <- seq(from = 5, to = 5, by = 5) # seq(from = 5, to = 20, by = 5) #seq(from = 5, to = 150, by = 5)

stm_model_manuals <- tibble(
  #repeat each topic number twice (once for overview and once for manual)
  n_topic = rep(topic_numbers, each = 1) ) %>%
  mutate(
  #Identification information
  Origin     = rep(c("manuals"), length(topic_numbers)),         
  `Topic ID` = paste(Origin, n_topic, sep = "_"),
  DTM        = pmap(.l = list(Origin), .f = extract_dtm),
  Model      = map(n_topic, .f = my_stm, manuals_corpus, manuals_covariates),

)
```

```{r}
topic_model_manual <- 
```
Inspection plots:
```{r plot STM}
select_topic_model <- function(origin, K){
  model <- stm_model %>% 
    filter(Origin == origin, n_topic == K) %>%
    pull(Model)

   model <- model[[1]]
}

>>>>

For `d_text` we keep only the most recent year.
```{r import data, eval = TRUE}
#load
load("./Output/d_text.RDATA")
```

@@

  STM_model <- stm(corpus$documents, corpus$vocab, data= data, prevalence = ~department, K = n_topics, init.type = "Spectral")
}
```
###mystm_manuals
```{r my_STM, eval= TRUE}
my_stm_manuals <- function(n_topics){

  STM_model <- stm(manuals_corpus$documents, manuals_corpus$vocab, data = manuals_covariates, prevalence = ~department, K = n_topics, init.type = "Spectral")
}
```
####My_stm_eval Function
This function applied stm but with heldout vocab and documents. 
```{r}
my_stm_eval <- function(heldout, n_topic){
  stm::stm(heldout$documents, heldout$vocab, n_topic, init.type = "Spectral")
}
```

@@

Manuals_ models do not work:
```{r models_manuals in tibble, error=TRUE}
topic_numbers <- seq(from = 5, to = 10, by = 5) # seq(from = 5, to = 20, by = 5) #seq(from = 5, to = 150, by = 5)

model_tmp_result <- vector("list", length(topic_numbers))

for(i in seq_along(topic_numbers)){
  k <- topic_numbers[[i]]
  model_tmp_result[[i]] <- stm(documents = manuals_corpus$documents, 
                               vocab = manuals_corpus$vocab, 
                               K = k, 
                               #data = manuals_covariates, 
                               #prevalence = ~department, 
                               init.type = "Spectral"
                               )
}
stm_model_manuals <- many_models(
  K = 5:10,
  documents = manuals_corpus$documents,
  vocab= manuals_corpus$vocab,
  prevalence = ~ department, 
  data = manuals_covariates,
  runs = 5
)

```{r}
topic_model_manual <- 
```
Inspection plots:
```{r plot STM}
select_topic_model <- function(origin, K){
  model <- stm_model %>% 
    filter(Origin == origin, n_topic == K) %>%
    pull(Model) %>%
    .[[1]]
}
